\section{Arithmetic Word Problems}

\bigskip
\textbf{General Equation}

\bigskip
\begin{equationbox}{Fraction Rules}
\setlength{\columnseprule}{0pt}
\begin{spacing}{1.5}
\begin{multicols}{3}
\[\frac{a\cdot c}{b\cdot c}=\frac{a}{b}\]

\[a\cdot \frac{b}{c}=\frac{ab}{c}\]

\[\frac{a}{b}\cdot\frac{b}{d}=\frac{ab}{cd}\]

\[\frac{a}{b}\div\frac{c}{d}=\frac{a}{b}\cdot\frac{d}{c}\]

\[\frac{a}{c}\pm\frac{b}{c}=\frac{a\pm b}{c}\]

\[\frac{a}{b}\pm\frac{c}{d}=\frac{ad\pm bc}{bd}\]
\end{multicols}
\end{spacing}
\end{equationbox}

\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item If 3 gallons of water fill 2 fish bowls, how many gallons will fill 9 fish bowls?

\vfill\item If $y$ varies directly as $x$, and $y=6$ when $x=9$, what is the value of $y$ when $x=12$?

\vfill\item Terri rides her bike every day on her way to school. On a sunny day, Terri can make the 2.6 mile trip in half of an hour at a constant pace. When it rains, Terri's speed drops by 1 mile per hour. If Terri's trip is the same distance in the rain, what total time it takes her to get to school?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 If the side length, $s$, of a square is increased by $n$, what is the ratio of the area of the new square to the old?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $n^2:1$
\2 $n^2:s^2$
\2 $s^2:n^2$
\2 $s^2:(s+n)^2$
\2 $(s+n)^2:s^2$

\midline

\1 From January to March, coats drop in price by 10\% each month from the month before. Which ratio represents the cost of the jacket from January to March?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $100:81$
\2 $10:81$
\2 $10:9$
\2 $9:1$
\2 $11:9$

\columnbreak
\advanced

\1 If $P$ varies jointly as $T$ and inversely as $V$, and $P=5$ when $V=3$, what is the value of $V$ when $P$ doubles and $T$ remains unchanged?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 1.5
\2 2.5
\2 6
\2 10
\2 12

\midline

\1 A jar contains $D$ jellybeans. If there are $A$ red jellybeans, $B$ green jellybeans, and $C$ orange jellybeans. What proportion of the jellybeans are red or orange?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $\frac{A+C}{A+B+C}$
\2 $\frac{A+C}{D}$
\2 $\frac{D-(A+C)}{D}$
\2 $\frac{D-B}{A+B+C}$
\2 $\frac{D-B}{D}$
\end{outline}
\end{multicols*}