\section{Rational Numbers}

\bigskip
\textbf{General Equation:} $\frac{a}{b}$ where $a$ and $b$ are integers and $b\neq0$

\vfill
\textbf{Example 1.} If $\frac{x}{3}=\frac{y}{5}$, write an inequality stating the relationship between $x$ and $y$.

\vfill
\textbf{Example 2.} If the number of microbes in a petri dish is reduced by a factor of one-third after each day, how many days will it take for the population to be less than 10\% of the original amount?

\vfill
\textbf{Example 3.} The batting average of a baseball player is given by the proportion of hits versus the number of times at bat. If Stanley has a batting average of 0.32 and had 24 hits in one season, what is the number of times Stanley was at bat?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 If the odds of choosing a red marble from a bag of marbles is 0.3. If the odds of choosing $n$ red marbles is 0.027, what is the value of $n$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2
\2 3
\2 6
\2 7
\2 9

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 One-third of Ms. Boyd's class takes French while four-fifths takes Spanish. How many students are taking both French and Spanish?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 1/15
\2 2/15
\2 1/5
\2 1/3
\2 2/3

\columnbreak
\centerline{\large ADVANCED}

\1 Bob is two-thirds the age of his sister Sally. If Sally is four-thirds times the age of their sister, Patricia. If Patricia is 3 years older than Bob, what is Sally's age?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 20
\2 24
\2 28
\2 32
\2 36

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 From 1970 to 2010, the population of US living on the coast has increased by approximately 40\%. If approximately 40\% of the total population of the USA lives on the coast in 2010 and the population in 2010 is 308 million people, what is the population (in millions) of the US in 1970?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 49
\2 77
\2 88
\2 193
\2 220
\end{outline}
\end{multicols*}