\section{Sequences and Series}

\bigskip
\textbf{General Equation:}

\bigskip
\begin{tabularx}{\textwidth}{*2{@{}>{\centering\arraybackslash}X}}
\textbf{Arithmetic Sequence} & \textbf{Geometric Sequence}\\
$a_n=a_n+nd$ & $a_n=a_1r^n$
\end{tabularx}

\vfill
\begin{tabularx}{\textwidth}{*2{@{}>{\centering\arraybackslash}X}}
\textbf{Arithmetic Series} & \textbf{Geometric Series}\\
$S=\frac{n(a_1+a_n)}{2}$ & $S=\frac{a_1(1-r^n)}{1-r}$
\end{tabularx}

\vfill
\textbf{Example 1.} Shelly is preparing to run for a marathon. If Shelly starts running on the first week with 1 kilometer, and doubles the number of kilometers every week, how many miles will she run on the sixth week?

\vfill
\textbf{Example 2.} Jenny receives a weekly allowance of \$15 and is saving up to buy a new laptop that costs \$450. If she has \$100 saved up already, how many days will it take her to have enough for the laptop?

\vfill
\textbf{Example 3.} A ball is dropped from a height of 1 meter and bounces a height of two-thirds of the previous bounce with every consecutive bounce. What is the total distance the ball has traveled after 5 bounces?

\vfill
\newpage
\begin{multicols*}{2}
\centerline{\large MEDIUM}

\begin{outline}[enumerate]
\1 Tom is doing a cross country bike ride. On the first day, Tom rode 5 miles. If he decides to ride an additional 20\% every day, approximately how long will he have ridden on day 8?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\2 13 miles
\2 14 miles
\2 17 miles
\2 19 miles
\2 20 miles

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip

\begin{spacing}{1.5}
\centerline{\begin{tabular}{|c|*3{>{\centering\arraybackslash}p{2em}|}}\hline
\textbf{Month} & 2 & 5 & 7\\\hline
\textbf{Height} & 5 & 9.5 & 11.5\\\hline
\end{tabular}}
\end{spacing}

\1 Eduardo purchases a potted plant to grow at home. The height is recorded (in inches) every month. If the rate of growth is constant, at what height did Eduardo buy the plant?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\2 2 in
\2 3 in
\2 3.5 in
\2 4 in
\2 4.5 in

\columnbreak
\centerline{\large ADVANCED}

\1 A spherical balloon deflates at a rate such that the volume is cut in half every 2 minutes. If $r$ is the initial radius, which expression represents the radius after 8 minutes?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $r/2$
\2 $r/4$
\2 $r/8$
\2 $r/16$
\2 $r/32$

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 A guitar string is plucked and the distance between the highest point and the lowest point of the first oscillation is 256 millimeters. If the distance the string travels is reduced by one-quarter with each oscillation, how many oscillations will it take for the string to have traveled a total distance of 700 millimeters?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2.5
\2 3
\2 3.5
\2 4
\2 5
\end{outline}
\pagebreak
\end{multicols*}