\section{Elementary Number Theory}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Quotient and Divisor Theorem}
For all integers $a$ and $b$,

\[a=q\cdot b+r\]

where $q$ is the quotient and $r$ is the remainder such that $r<b$.

\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Gumdrops come in bags of 60. Mr. Lee wants to buy enough bags so that he has a perfect square number of gumdrops. What is the least number of bags Mr. Lee will need to buy?

\vfill\item The sum of the angles of a regular polygon is given by the equation $S(n)=180(n-2)$ where $n$ is the number of sides. How many sides does the smallest regular polygon have if is the smallest regular polygon possible such that each individual angle is over $120^\circ$?

\vfill\item A group of 10 students participate in a math competition. The students are required to shake hands with all other participates in the competition. If each handshake between two people is counted only once, how many distinct handshakes are there overall?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 There are $n$ jellybeans in a jar. The number of jellybeans can be separated into groups of 24 or groups of 42. What is the least possible number of jellybeans in the jar?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 126
\2 168
\2 252
\2 504
\2 1008

\midline

\1 A full revolution of the hour hand around the face of a clock corresponds to 12 hours. If the hour hand starts at 12:00 AM and completes 6.75 revolutions, what is the current time?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 3:00 AM
\2 9:00 AM
\2 3:00 PM
\2 6:00 PM
\2 9:00 PM

\columnbreak
\advanced

\1 If $f$ is the number of faces of a cube, $v$ is the number of vertices, and $e$ is the number of edges, what is the value of $v-e+f$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\2 0
\2 1
\2 2
\2 6
\2 12

\midline

\1 Ms. Rizzo has a box of sand in her classroom. If the value of the volume is a positive integer greater than 1 in$^3$ that is both a perfect square and a perfect cube, what is the surface area of the closed box?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 6
\2 32
\2 64
\2 72
\2 96
\end{outline}
\end{multicols*}