\section{Counting Techniques}

\bigskip
\textbf{General Equation}

\bigskip
\begin{equationbox}{Permutations and Combinations}
When choosing $r$ items from $n$ items,

\bigskip
\renewcommand{\arraystretch}{1.15}
\setlength{\fboxsep}{0pt}
\colorbox{white}{
\begin{tabularx}{\textwidth}{@{}|*2{>{\centering\arraybackslash}X|}}\hline
\textbf{\large Permutations} & \textbf{\large Combinations}\\
When order matters & When order does not matter\\\hline
\textit{Without Repetition} & \textit{Without Repetition}\\
$_nP_r=\frac{n!}{(n-r)!}$ & $_nC_r=\frac{n!}{r!(n-r)!}$\\[1.5em]
\textit{With Repetition} & \textit{With Repetition}\\
$n^r$ & $\frac{(n+r-1)!}{r!(n-1)!}$\\[2ex]\hline
\end{tabularx}}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Mandy is throwing an ice cream party and has 3 flavors of ice cream and 4 different toppings. How many different combinations can her guests make?

\vfill\item Jerry is making a sundae with 3 scoops of ice cream. If he has 5 flavors of ice cream, how many different combinations can Jerry make if he can only use each flavor once?

\vfill\item If a four-digit pin number contains the digits 0 to 9 where no digit can be repeated more than twice, how many different combinations for pin numbers are possible?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 If set A contains all even integers under twenty and set B contains all even prime numbers, then the set of common elements between set A and set B is

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 \{\}
\2 \{0\}
\2 \{2\}
\2 \{0, 2\}
\2 All even numbers

\midline

\1 If a four point star has 8 vertices, and an eight point star has 16 vertices, how many vertices does a 10 point star have?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 12
\2 16
\2 20
\2 24
\2 32

\columnbreak
\advanced

\1 A number of volleyballs compete in a tournament. If each team must play one another, and there are a total of 120 matches, how many teams competed?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 5 teams
\2 6 teams
\2 7 teams
\2 8 teams
\2 12 teams

\midline

\1 An equilateral triangle is divided so that the midpoint of each line is the vertex of an inscribed triangle. If the process continues, how many triangles will there be after $n$ divisions?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $2^n$
\2 $3^n$
\2 $4^n$
\2 $4n$
\2 $8n$
\end{outline}
\end{multicols*}