\section[Algebraic Expressions]{Substitution and Simplifying Algebraic Expressions}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Algebraic Properties}
\setlength{\columnseprule}{0pt}
For all real numbers $a,\ b$, and $c$,

\begin{center}
\begin{multicols}{2}
\textbf{Distributive Property}

$a(b+c)=ab+ac$

\columnbreak
\textbf{Transitive Property}

If $a=b$ and $b=c$, then $a=c$
\end{multicols}
\end{center}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item If Sally has 6 boxes and each box has 12 books, how many books does Sally have?

\vfill\item Chase and Jill both collect stamps. If Jill has six less than twice the number of stamps than Chase does, how many stamps does Jill have if Chase has 24 stamps?

\vfill\item Townsville High School has 30 classrooms, each with 15 desks. If 80\% of desks are filled in 90\% of the classrooms and the other 10\% of the classrooms are 100\% full, how many students attend the school?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 Chris has a collection of 120 records which consists of jazz, blues, and classical records. If one-fourth of the records are jazz and one-third of the records are blues, how many of the records are classical?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 30
\2 40
\2 50
\2 60
\2 70

\midline

\1 The density, $d$, of an object is the ratio of its mass to its volume. If the volume of an object is halved and the mass is doubled, which expression represents the new density in terms of $d$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $1/4d$
\2 $1/2d$
\2 $d$
\2 $2d$
\2 $4d$

\columnbreak
\advanced

\1 Tommy is on the outer edge of a merry-go-round that moves at a constant speed. If $r$ is Tommy's distance from the center, and the merry-go-round makes $m$ full cycles during $n$ minutes, which expression represents Tommy's distance traveled in 1 hour?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $\frac{mr\pi}{30n}$
\2 $\frac{mr^2\pi}{30n}$
\2 $\frac{120r\pi}{mn}$
\2 $\frac{120mr^2\pi}{n}$
\2 $\frac{120mr\pi}{n}$

\midline

\1 Bunny Slopes Co. is having a sale on winter wear of 20\% off. Tracy buys a pair of ski goggles and receives an additional 10\% off of the sale price. If the final cost of the goggles is \$90, how much did Tracy save?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 22
\2 25
\2 35
\2 38
\2 125
\end{outline}
\end{multicols*}