\section[System of Equations]{Systems of Equations and Inequalities}

\bigskip
\textbf{General Equation}

\bigskip
\begin{equationbox}{Special Linear Relationships}
\textbf{Definition:} A system of linear equations is said to be independent if there are 0 points of intersection between the graph of each equation (parallel lines).

\bigskip
A system of linear equations is said to be dependent if there is 1 point of intersection or infinitely many points of intersection (overlapping lines).

\bigskip
Two lines can only intersect 0, 1, or infinitely many times.
\end{equationbox}
 
\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Plane A and plane B are flying parallel to one another. If after 20 minutes, plane A has risen an altitude of 2000 m, how much has the altitude of plane B has risen in 30 minutes?

\vfill\item When Johnny has $x$ nickels and $y$ dimes, his total is \$3. When he has $y$ nickels and $x$ dimes, his total increases by \$0.75. How many nickel and dimes did Johnny start off with?

\vfill\item If the point $P(3,1)$ is on a line that passes through the origin, what is the $y-$intercept of the perpendicular line that passes through $P$?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 A coffee costs \$2.5 and a muffin costs \$3. If Tasha has \$11 and makes a purchase, what is the least amount of change she can receive?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 \$0.00
\2 \$0.50
\2 \$1.00
\2 \$1.50
\2 \$2.00

\midline

\1 Stacy and Ann compete in a relay race that consists of 3 events, each with a highest possible score of 10 points. If Stacey earned 8 points and 9 points in the first two events, what is the least number of points she will need to earn in the third event to win if Ann received received a 23 points total?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 6
\2 7
\2 10
\2 23
\2 24

\columnbreak
\advanced

\1 Two planes leave from the same terminal heading in the same direction. If plane A travels at 400 mph, and plane B travels 600 mph 4 hours after the departure of the first plane, how many hours from the departure of the first plane will the planes be adjacent?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2
\2 8
\2 4
\2 12
\2 48

\midline

\1 A coyote is chasing a roadrunner in a parallel path. If the roadrunner and coyote are running at a constant rate of 30 mph and the roadrunner has a 20 mile gain on the coyote, how much faster will the coyote need to run if he is going to catch up to the roadrunner in 2 hours?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 10 mph
\2 20 mph
\2 25 mph
\2 30 mph
\2 40 mph
\end{outline}
\end{multicols*}