\section{Equations of Lines}

\bigskip
\textbf{General Equation:}

\begin{center}
Slope-Intercept Form of a Line

$y=mx+b$
\end{center}

\vfill
\textbf{Example 1.} Sunshine taxi charges a base fare of \$2.60 and \$0.40 for every quarter mile. If Elle's ride is 5 miles, how much is her ride?

\vfill
\textbf{Example 2.} A parking lot charges \$10 for the first 4 hours and \$2 up to every additional hour. If George leaves his car for 8 and a half hours, how much is he charged?

\vfill
\textbf{Example 3.} Moe's dad will give him \$1 for every $x$ points over 50 on his math test, where $x$ is a whole number of points. Moe received 86 points on his math test and earned \$12. How many points does Moe need to earn \$1?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 Travis is a car salesman and earns \$10 an hour plus a flat commission fee for each car he sells. If Travis works 30 hours and has earned \$1,000 in a week, how much does Travis earn in commission per car if he sells 4 cars?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 80
\2 160
\2 320
\2 360
\2 640

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 Cherry is setting up a can drive at her school. For every 50 cans after 100 she collects, the donation center will give her one ticket to an amusement park. If Cherry wants a total of 10 tickets, what is the least number of cans she will need to collect?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 500
\2 600
\2 1050
\2 1500
\2 5100

\columnbreak
\centerline{\large ADVANCED}

\1 The value of a car depreciates every year at a constant rate of $p$\% of the total value. If the initial value of the car is $d$ dollars, what is the current value of the car after $m$ months?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $d-pm$
\2 $d-\frac{pm}{12}$
\2 $d-\frac{pm}{100}$
\2 $d-\frac{pm}{1200}$
\2 $d\left(1-\frac{pm}{1200}\right)$

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}
\1 The value of an interior angle of a regular $n$-gon increases as a linear function of $n$. If an interior angle of a 4-gon is $90^\circ$ and a 6-gon is $120^\circ$, what is the sum of all interior angles of an $n$-gon whose interior angles are each $144^\circ$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 10
\2 12
\2 144
\2 576
\2 1440
\end{outline}
\end{multicols*}