\section{Properties of Exponents}

\bigskip
\textbf{General Equation:} 

\centerline{The Laws of Exponents}

\begin{spacing}{2}
\begin{tabularx}{\textwidth}{*2{@{}>{\centering\arraybackslash}X}}
$a^m\cdot a^n = a^{m+n}$ & $\frac{a^m}{a^n}=a^{m-n}$\\
$(ab)^m=a^m\cdot b^m$ & $(a^m)^n=a^{mn}$
\end{tabularx}
\end{spacing}

\vfill
\textbf{Example 1.} There are 1000 milimeters in one meter and 1000 meters in one kilometer. How many times larger is a kilometer than a millimeter?

\vfill
\textbf{Example 2.} A pallet contains 5 rows of 5 columns of boxes, each column 5 boxes high. How many boxes does the pallet contain?

\vfill
\textbf{Example 3.} The intensity of a sound is inversely proportional to the square of your distance from the source of the sound. If  you are 6 times further away from a set of speakers at a concert as your friend, what is the ratio of the intensity of you to your friend?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 A wooden block occupies a volume of $2a$. If the side length is an integer, what is the smallest possible value of $a$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2
\2 3
\2 4
\2 8
\2 16

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 The sum of the squares of two numbers, $a$ and $b$, is equal to to the square of the sum. Which of the following must be true?

\begin{enumerate}[label=\Roman*.]
\item $a\cdot b=0$
\item $a=b$
\item $(a+b)^3=a^3+b^3$
\end{enumerate}

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 I is true
\2 II is true
\2 III is true
\2 I and II is true
\2 I, II, and III are true

\columnbreak
\centerline{\large ADVANCED}

\1 The distance of an object falling from height is proportional to the square of time of the fall. If Betty drops a rock from the top of a building, the rock travels a distance of $d^3$ meters after time $t$ seconds. If both the distance and the time are whole numbers and $d\neq t$, what is the least distance traveled by the rock?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2 m
\2 4 m
\2 8 m
\2 32 m
\2 64 m

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}
\1 A coat goes on sale x percent off of the original sale price every month. Which of the following expressions represents the amount taken off after $m$ months?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $n\left(\frac{x}{100}\right)^m$
\2 $n\left[1-\left(\frac{x}{100}\right)^m\right]$
\2 $1-\left(\frac{x}{100}\right)^m$
\2 $n\left[1-\left(\frac{x^m}{100}\right)\right]$
\2 $n(1-x^m)$
\end{outline}
\pagebreak
\end{multicols*}