\section{Quadratic Equations}

\bigskip
\textbf{General Equation}

\bigskip
\begin{equationbox}{Vertex Equation}
If $f(x)$ is a quadratic functions with roots $r$ and $s$, then the coordinate of the vertex (maximum or minimum) is

\[\left(\frac{s-r}{2},\ f\left(\frac{s-r}{2}\right)\right)\]

\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Reese jumps, starting from the ground, and reaches a maximum height of 6 feet at 3 seconds. How long does the trip take from when she first jumped until she returned back to the ground?

\vfill\item The height in feet of a cannonball fired into the air from ground-level is a function of time in seconds. If the cannon hits the ground after $t$ seconds and the maximum height is $h$ ft, state the coordinate that expresses the maximum of the cannonball's trajectory.

\vfill\item The sum of two integers $x$ and $y$ is 9 and the product of the two integers is 20. What is the value of $|x^y-y^x|$?
\end{enumerate}

\vfill
\newpage
\begin{multicols}{2}
\begin{outline}[enumerate]
\medium

\1 Stacey is making a rectangular garden for her rose bushes. If the perimeter needs to be 100 cm, what is the maximum area she can enclose?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 25 cm$^2$
\2 50 cm$^2$
\2 100 cm$^2$
\2 500 cm$^2$
\2 625 cm$^2$

\midline

\1 For two integers $p$ and $q$, the sum of their squares is equal to the square of their sum. What is the value of $pq$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0
\2 1
\2 2
\2 3
\2 4

\columnbreak
\advanced

\1 The height, in meters, of a ball thrown from the ground as a function of time, in seconds is modeled by equation $f(t)=-x^2+2x$. What is the equation of the line passing through the coordinate of the maximum of $f(t)$ and the and the coordinate given by the time when the ball returns to the ground.

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $y=-x+2$
\2 $y=x+2$
\2 $y=-x+1$
\2 $y=x-1$
\2 $y=2x-1$

\midline

\1 Andres has 8 kilometers of fencing for his goats and sheep. If he builds a single rectangular pen for both, what is the length of the shortest side in meters? (1 kilometer = 1000 meters)

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 100 m
\2 300 m
\2 400 m
\2 600 m
\2 1000 m
\end{outline}
\end{multicols}