\section{Systems of Equations and Inequalities}

\bigskip
\textbf{General Equation:} 

\bigskip
\begin{tabularx}{\textwidth}{*2{@{}>{\centering\arraybackslash}X}}
Parallel Lines & Perpendicular Lines\\
$m_1 = m_2$ & $m_1 \cdot m_2 = -1$
\end{tabularx}

\vfill
\textbf{Example 1.} Plane A and plane B are flying parallel to one another. If after 20 minutes, plane A has risen an altitude of 2000 m, how much has the altitude of plane B has risen in 30 minutes?

\vfill
\textbf{Example 2.} When Johnny has $x$ nickels and $y$ dimes, his total is \$3. When he has $y$ nickels and $x$ dimes, his total increases by \$0.75. How many nickel and dimes did Johnny start off with?

\vfill
\textbf{Example 3.} Two cars starting at the same intersection begin traveling perpendicular to one another. If the first car travels north west at a $25^\circ$ angle of the point of intersection, what is the direction of the second car?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 A coffee costs \$2.5 and a muffin costs \$3. If Tasha has \$11 and makes a purchase, what is the least amount of change she can receive?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 \$0.00
\2 \$0.50
\2 \$1.00
\2 \$1.50
\2 \$2.00

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 Stacy and Ann enter a relay race that consists of 3 events, each worth 10 points. If Stacey earned 8 points and 9 points in the first two events, how what is the smallest number of points she will need to earn in the third event to win if Ann received received a 23 points total?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 6
\2 7
\2 10
\2 23
\2 24

\columnbreak
\centerline{\large ADVANCED}

\1 Two planes leave from parallel terminals. If plane A travels north west at 400 mph, and plane B travels north west 600 mph 4 hours later, by what time will the second plane have equal distance traveled as the first plane?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2
\2 8
\2 4
\2 12
\2 48

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}
\1 A coyote is chasing roadrunner in a parallel path. If the roadrunner and coyote are running at a constant rate of 30 mph and the roadrunner has a 20 mile gain on the coyote, how much faster will the coyote need to run if he is going to catch up to the roadrunner in 2 hours?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 10 mph
\2 20 mph
\2 25 mph
\2 30 mph
\2 40 mph
\end{outline}
\pagebreak
\end{multicols*}