\section[Algebraic Functions]{Concepts of Algebraic Functions}

\bigskip
\textbf{General Equation}

\bigskip
\begin{equationbox}{Coordinates}
\textbf{Definition:} If $f(a)=b$, then $(a,b)$ is a coordinate of the graph of $f$.
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item If Timmy sells less lemonade in week $x$ than in week $y$ and Timmy's sales has increased every week, what relationship describes $y$ to $x$?

\vfill\item Luckystar is a horse that races in the Belmont racetrack. If Luckystar runs at $x$ mph at time $p$ and again at time $q$, what is his increase in average speed over the interval from $p$ to $q$?

\vfill\item If Arnold has $3\times3, 4\times4$, and $5\times5$ cubes, what is the least number of cubes Arnold will need to make a building that is 27 units high?

\vfill\item Lindsey and Ricky have separate college tuition funds created on a Monday. Lindsey's account starts at an initial amount of \$0.50 and the total doubles every day, whereas Ricky's college tuition starts at \$1 initially and the total doubles every day. On what day will Lindsey begin having greater amounts in her account than Ricky will have in his account?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 If the amount of bacteria in a colony doubles every hour, which of the following cannot be a relative factor of the population of bacteria?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 1/2
\2 0
\2 1
\2 2
\2 8

\midline

\1 $f$ has the property that $f(\square)=\clubsuit$ and $f(\clubsuit)=\square$ for all $\clubsuit$ and $\square$. Which of the following represents the equation for $f$ in terms of $x$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $f(x)=x$
\2 $f(x)=x^2$
\2 $f(x)=0$
\2 $f(x)=1$
\2 $f(x)=\sqrt{x}$

\columnbreak
\advanced

\1 The odds of choosing a prime number out of $x$ terms is $m$ and the odds of choosing and even number out of the same $x$ terms is $n$. What are the odds of choosing an even prime out of $x^2$ terms?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $1/mn$
\2 $1/x$
\2 $1/x^2$
\2 $1/(m+n)$
\2 Cannot be determined

\midline

\1 If Kat is on a swing that starts at a height of $h$ off the ground and reaches the ground after $t/3$ seconds, at what position will she be at $15t$ relative to her beginning position?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $h$
\2 $-h$
\2 0
\2 $2h$
\2 $-2h$
\end{outline}
\end{multicols*}