\section{Direct and Inverse Variation}

\bigskip
\textbf{General Equation:} 

\begin{center}
\setlength{\columnseprule}{0pt}
\begin{multicols}{2}
Direct Variation

$y=kx$

\columnbreak
Joint Variation

$xy=k$
\end{multicols}
\end{center}

\vfill
\textbf{Example 1.} If there are approximately 30 centimeters in one foot, how many centimeters are there in 18 inches? (1 foot = 12 inches)

\vfill
\textbf{Example 2.}  When a delivery truck carries heavier packages, the speed of the truck decreases. If the truck is able to go 60 mpg when it carries 400 lbs, how much time will it take the truck to carry 600 lbs and travel 100 miles?

\vfill
\textbf{Example 3.} The speed of a vehicle increases as the amount of fuel used increases, and the amount of time spent traveling over a fixed distance decreases. If a vehicle goes 30 miles an hour for 60 minutes using one gallon of gasoline, how much gasoline will be required to speed the vehicle by 30 miles per hour for 45 minutes?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 The area of a square is proportional to the length of the diagonal. If $d$ is the area, which of the following describes the area in terms of $d$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $d^2$
\2 $(d\sqrt2)^2$
\2 $(d/\sqrt2)^2$
\2 $d^2\sqrt2$
\2 $\sqrt2d^2$

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 The measure of acidity, pH, of a compound is proportional inversely proportional to the compound's hydroxide concentration, [OH$^-$]. If the pH is 4 when [OH$^-$] is $10^{-10}$, what is the pH decreased by when the [OH$^-$] is decreased by a factor of 10?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 1
\2 3
\2 4
\2 30
\2 40

\columnbreak
\centerline{\large ADVANCED}

\1 The odds of guessing a number correctly are proportional to the number of terms to guess from. If the odds of choosing $p$ numbers out of $q$ terms is 0.4, what are the lease odds of choosing $p$ out of $q+1$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0.3
\2 0.33
\2 0.36
\2 0.375
\2 0.38

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}
\1 The volume, $V$, of a right cylinder is directly proportional to its radius and height. If the radius is doubled and the height is halved, what is the new volume in terms of the old volume, $V$? ($V=\pi r^2h$)

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $V/4$
\2 $V/2$
\2 $V$
\2 $2V$
\2 $4V$
\end{outline}
\pagebreak
\end{multicols*}