\section[Volumes]{Volume of a Box, Cube, and Cylinder}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Volume Equations}
\setlength{\columnseprule}{0pt}

\begin{center}
\begin{multicols}{3}
\textbf{Volume of a Box}

$V=l\times w\times h$

\textbf{Volume of a Cube}

$V=s^3$

\textbf{Volume of a Cylinder}

$V=\pi r^2h$
\end{multicols}
\end{center}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Kallie is filling her bookshelf with books that are $8\times5\times2$ in\textsuperscript{3}. If Kallie has 16 such books, how much volume do the books occupy?

\vfill\item A large cube is made by stacking smaller $4\times4$ cubes. What is the total volume of the large cube?

\vfill\item Pete stacks pizza pies on each other in a freezer for later heating. The pizzas are 2 inches thick and have a diameter of 16 inches. What volume do 10 pizzas occupy?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 A rectangular box has a volume of 36 in\textsuperscript{3} If cubes of side length 2 are placed into the rectangular box, what is the least amount of volume of the box not filled by the cubes?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0 in\textsuperscript{3}
\2 2 in\textsuperscript{3}
\2 4 in\textsuperscript{3}
\2 6 in\textsuperscript{3}
\2 8 in\textsuperscript{3}

\midline

\1 A cylinder is placed in a rectangular box so that the diameter of the cylinder is the width and height of the rectangle. What is the ratio of volume of the cylinder to the volume of the box?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $4-\pi$
\2 $\frac{4}{\pi}$
\2 $\frac{\pi}{4}$
\2 $\frac{8}{\pi}$
\2 $\frac{\pi}{8}$

\columnbreak
\advanced

\1 A cube of volume $V$ of integer side length $s$ is split into 6 smaller rectangular boxes of equal volume. What is the value of $V$ if it is the smallest such cube?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 6
\2 36
\2 64
\2 125
\2 216

\midline

\1 Cubic blocks are stored in a cylindrical container so that the diagonal length of the cube is the diameter length of the cylinder. If the height of the cylinder is 5 times the radius, what is the most number of cubes that fit into the cylinder?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 1
\2 2
\2 3
\2 4
\2 5
\end{outline}
\end{multicols*}