\section[Special Triangles]{Pythagorean Theorem and Special Properties of Isosceles, Equilateral, and Right Triangles}

\textbf{General Equation}

\bigskip
\begin{equationbox}{The Pythagorean Theorem}
\begin{center}
In a right triangle, if $a$ and $b$ are the side lengths of the triangle and $c$ is the length of the hypotenuse, then

\bigskip
$a^2+b^2=c^2$
\end{center}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item The perimeter of an equilateral triangle is 16 cm. What is the triangle's area?

\vfill\item Gretchen and Samuel leave school. Gretchen walks $45^\circ$ due south west and Samuel walks $45^\circ$ due south east. If they each live a quarter mile away from school, what is the distance between their houses?

\vfill\item A 13 ft ladder is propped up against a wall. If the base of the ladder to the base of the wall is equidistant from the top of the ladder to the base of the wall, what is the difference between the length of the ladder and the base of the ladder to the base of the wall?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 The area of an equilateral triangle is 16 cm\textsuperscript{2}. What is the triangle's perimeter to the nearest hundredth?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:} 

\vfill
\2 3.04
\2 6.07
\2 6.08
\2 18.23
\2 18.24

\midline

\1 The ratio of the sides of a right triangle are in a proportion of $3:4:5$ where $x$ is the proportion of the longest side. If the hypotenuse is 27 units long, what the area of the triangle to the nearest whole number?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 72
\2 65
\2 175
\2 162
\2 243

\columnbreak
\advanced

\1 The hypotenuse of a right triangle is twice as long as the shortest side. If the length of the longer leg is 10 cm, what is the perimeter of the triangle?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $10+10\sqrt{3}$
\2 $20+\sqrt{3}$
\2 $20+10\sqrt{3}$
\2 $30+10\sqrt{3}$
\2 30

\midline

\1 The side lengths of a rectangle are in a proportion of $a:a+4$. If the perimeter is 76 sq. units, what is the length of the diagonal to the nearest whole number?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 12 units
\2 16 units
\2 24 units
\2 27 units
\2 40 units
\end{outline}
\end{multicols*}