\section{Rational and Radical Equations}

\bigskip
\textbf{General Equation:}

\bigskip
If $\frac{a}{b}=\frac{c}{d}$, then

\bigskip
\begin{itemize}[label=$\bullet$]
\item $ad=bc$

\bigskip
\item $\frac{a}{c}=\frac{b}{d}$
\end{itemize}

\vfill
\textbf{Example 1.} If the sequence $x$, \shortline, $y$ has a common ratio between each term, what is the value of the missing term?

\vfill
\textbf{Example 2.} A three digit number is evenly divided by a two digit number such that the quotient is a perfect square. What is the smallest such three digit number and two digit number pair?

\vfill
\textbf{Example 3.} For an integer $n$, the square root and cube root are both integers. If the square root and cube root of $n$ are distinct, what is the smallest sum of both roots of such a number?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 The odds of choosing a red marble is 1 out of $p$ marbles and the odds of choosing a green marble is 1 out of $q$ marbles. Which expression represents the odds of choosing a red or a green marble?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $(p+q)/pq$
\2 $1/pq$
\2 $2/pq$
\2 $p+q$
\2 $(1-p)(1-q)$

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 Benjamin is missing cards in his deck of cards. If in his deck of 50 cards there are $x$ kings and $y$ queens. What are the odds of choosing a queen and a king?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $xy/50$
\2 $(x+y)/50$
\2 $2500/xy$
\2 $(x+y)/2500$
\2 $xy/2500$

\columnbreak
\centerline{\large ADVANCED}

\1 The ratio of the sides of a rectangle is $a:b$. If one is added to both sides, the new ratio of sides is $b:a$. Which of the following must be true?

\begin{enumerate}[label=\Roman*.]
\item The rectangle is a square
\item The area is $a^2$
\item The side length is 1
\end{enumerate}

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 I is true
\2 II is true
\2 III is true
\2 I and II are true
\2 I, II, and III are true

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}
\1 A square is inscribed in a circle. If the radius of the circle double, by what factor does the side length of the square grow?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 2
\2 $\sqrt2$
\2 4
\2 $2\sqrt2$
\2 $4\sqrt2$
\end{outline}
\pagebreak
\end{multicols*}