\section[Polygons]{Area and Perimeter of a Polygon}
\textbf{General Equation:}

\begin{center}
\begin{multicols}{2}
\setlength{\columnseprule}{0pt}
Area

The measure of the surface of a two-dimensional shape

Perimeter

The measure of the distance around a two-dimensional shape
\end{multicols}
\end{center}

\vfill\textbf{Example 1:} The lengths of an $n$-sided figure are each doubled. If the perimeter of the original $n$-sided figure was $P$, what is the value of the new perimeter?

\vfill\textbf{Example 2:} A circle inscribed in a box has a radius equal to half of the diameter of the box. What area of the circle is not in the square if the radius is 1?

\vfill\textbf{Example 3:} A pizza box has a perimeter that is 1.5 times the circumference of the pizza. If the pizza has a diameter of 16 inches, what is the difference between the perimeter of the box and the circumference of the pizza?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 A square is inscribed in a circle. If the area of the square is 9 sq. in., what is the difference between the circumference of the circle and the perimeter of the square?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $3\sqrt{2}\pi-12$
\2 $12-3\sqrt{2}\pi$
\2 $6\sqrt{2}\pi-12$
\2 $12-6\sqrt{2}\pi$
\2 $3$

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 A right triangle has an area of $b$ sq. units. If a rectangle has a height equivalent to the height of the right triangle, and a base equivalent to twice the base of the right triangle, what is the area of the rectangle in terms of $a$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $a$
\2 $2a$
\2 $4a$
\2 $a^2$
\2 $2a^2$

\columnbreak
\centerline{\large ADVANCED}

\1 A rectangle whose width is twice its height is inscribed in a semicircle whose radius is equal to width of the rectangle. If $h$ is the height of the rectangle, which expression represents the area of the semicircle not in the area of the rectangle?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $2w^2(\pi-1)$
\2 $2w^2(9w^2\pi-1)$
\2 $2w^2(2\pi-1)$
\2 $2w^2(2\pi-1)$
\2 $w^2(\pi-2)$

\centerline{\rule{0.4\textwidth}{1pt}}

\1 Triangle $A$ is inscribed in equilateral triangle $B$ so that the vertices of $A$ are the midpoints of the sides of $B$. If the area of $B$ is 12 sq. units, what is the area of the $B$ with $A$ removed?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 6 sq. units
\2 7 sq. units
\2 8 sq. units
\2 9 sq. units
\2 12 sq. units
\end{outline}
\end{multicols*}