\section[Linear Relationships]{Properties of Parallel and Perpendicular lines}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Parallel and Perpendicular Lines}
\setlength{\columnseprule}{0pt}
For lines $L_1$ and $L_2$ with slopes $m_1$ and $m_2$ respectively

\begin{center}
\begin{multicols}{2}
\textbf{Parallel Lines}

$m_1=m_2$

\columnbreak
\textbf{Perpendicular Lines}

$m_1\cdot m_2=-1$
\end{multicols}
\end{center}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Two planes are traveling parallel to one another. If the first plane travels in a direction 30 miles north and 40 miles east of where it began, and the second plane travels 60 miles north of where it began, how far east must it travel in order to remain parallel to the first plane?

\vfill\item Two cars starting at the same location are traveling perpendicular to one another. What is the distance between the two cars if the first car has traveled 30 miles in one hour and the second car has traveled 40 miles in one hour?

\vfill\item A frog's tongue shoots straight up into the air to catch a fly that is flying horizontally. If the distance from the fly's speed is 6 meters per second and the speed between the frog and the fly is 20 meters per 2 seconds, how fast must the frog's tongue move in order to catch the fly?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 Roads A and B are parallel roads. If Road C runs perpendicular to road A, which of the following must be true?

\begin{enumerate}[label=\Roman*.]
\item Road C is perpendicular to Road B
\item Road A and C form a $90^\circ$ angle
\item The distance between Road A and Road B is uniform
\end{enumerate}

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 I only
\2 II only
\2 III only
\2 I and II are true
\2 I, II, and III are true

\midline

\1 Two dogs are running perpendicular paths, starting at the same location. If the first dog runs $m$ meters in 5 minutes, and the second dog runs $m$ meters in 10 minutes, which of the following represents the distance between the dogs after 10 minutes?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $m\sqrt{2}$
\2 $m\sqrt{3}$
\2 $\sqrt{2m^2+m^2}$
\2 $\sqrt{\frac{m}{2}^2+m^2}$
\2 $\sqrt{4m^2+m^2}$

\columnbreak
\advanced

\1 A set of parallel roads runs perpendicular to a second set of parallel roads. If the distance between each intersection along the road is at most $m$ km, which of the following cannot be the distance between diagonal intersections?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $m$
\2 $2m$
\2 $\frac{m}{2}$
\2 $\frac{m\sqrt{2}}{2}$
\2 $m\sqrt{2}$

\midline

\1 A pair of parallel chords are inscribed in a circle, equidistant from the center. If the distance between the chords is equal to the radius, $r$, what is the length each chord in terms of $r$?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 $\frac{r\sqrt{3}}{2}$
\2 $r\sqrt{3}$
\2 $\frac{3r^2}{4}$
\2 $r$
\2 $2r$
\end{outline}
\end{multicols*}