\section{Slope}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Slope}
\textbf{Definition:} Slope indicates the steepness of a line. The slope is denoted as a ratio of the rise over the run of a line, or the change in the vertical distance over the change in the horizontal distance between any two points on a line. For two points $(x_1,y_1)$ and $(x_2,y_2)$, the slope, $m$, is

\[m=\frac{\textrm{change in }y}{\textrm{change in }x}=\frac{\Delta y}{\Delta x}=\frac{y_2-y_1}{x_2-x_1}\]
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Points $(2,3)$ and $(5,k)$ lie on the line $3x-my=6$. What is the value of $k$ in terms of $m$?

\vfill\item What is the slope of the line formed when connecting the minute hand and the hour hand on a clock at 9 am if the distance between them is twice the length of the hour hand?

\vfill\item A toy rocket is launched from the ground at a $60^\circ$ angle into the air. Assuming the rocket travels a straight path, what is the slope of its path from the ground to its maximum?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 A ski lift travels 1500 feet at a $60^\circ$ angle of elevation to the top of a mountain. What is the slope of the path that the ski lift travels?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $\sqrt3/3$
\2 $1/2$
\2 $\sqrt3/2$
\2 $2\sqrt3/3$
\2 $\sqrt3$

\midline

\1 If the line $3x+ky=8$ passes through point $(-4,5)$, what is the value of $k$?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $-4/5$
\2 $7/4$
\2 4
\2 5
\2 $23/4$

\columnbreak
\advanced

\1 An equilateral triangle is drawn in the first quadrant with coordinates $(0,0)$ and $(6,0)$. What is the slope of the line formed from the point at the origin to the third point?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 $1/2$
\2 $\sqrt3$
\2 $2$
\2 $3$
\2 $6$

\midline

\1 $L_1$ and $L_2$ are two lines with slopes  $m_1$ and $m_2$ respectively. If $m_1\cdot m_2=1$, which of the following cannot be true?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2 $L_1$ and $L_2$ are parallel lines
\2 $L_1$ and $L_2$ are intersecting lines
\2 $L_1$ and $L_2$ are perpendicular lines
\2 $L_1$ and $L_2$ are coinciding lines
\2 $m_1$ and $m_2$ are reciprocals
\end{outline}
\end{multicols*}