\section{Similarity}

\textbf{General Equation:} Two polygons are similar if all corresponding sides are in proportion.

\vfill\textbf{Example 1:} Square ABCD and square EFGH have side lengths in a ratio of $1:2$. What percentage increase is the area of EFGH to ABCD?

\vfill\textbf{Example 2:} Line segment DE is drawn in triangle ABC so that D is the midpoint of AB and E is the midpoint of AC. What is the ratio of the areas of ADE to EDBC?

\vfill\textbf{Example 3:} Two concentric circles are drawn such that the radius of the outer circle is twice the diameter of the inner circle. What percentage is the circumference of the outer circle to the circumference of the inner?

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\centerline{\large MEDIUM}

\1 Right triangle BDC is similar to triangle ABC as shown below.

\begin{tikzpicture}
\draw (0,0) node[left] {A} -- (3,3) node[above] {B} node[midway,left] {15} -- (5,0) node[right] {C} node[midway, right] {10} -- cycle;
\draw (3,3) -- (3,0) node[below] {D};
\draw (3,0.2) -- (3.2,0.2) -- (3.2,0);
\draw (2.8,2.8) -- (3,2.55) -- (3.15,2.75);
\end{tikzpicture}

If AB = 15 and BC = 10, what is the length of BD?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 
\2 
\2 
\2 
\2 

\bigskip
\centerline{\rule{0.4\textwidth}{1pt}}

\bigskip
\1 An equilateral triangle is inscribed in another so that only the vertices of the inner triangle touch the edges of the outer. What is the greatest possible ratio of the area of the smaller triangle to the bigger one?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 
\2 
\2 
\2 
\2 

\columnbreak
\centerline{\large ADVANCED}

\1 The circumference of a children's basketball is 27.5 inches whereas the circumference of an NBA basketball is 29.5 inches. What is the ratio of their volumes?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 
\2 
\2 
\2 
\2 

\centerline{\rule{0.4\textwidth}{1pt}}

\1 A cube volume 64 cm$^3$ is made of smaller cubes, each with a volume of 8 cm$^3$. What is the ratio of the diagonals of the smaller cube to the entire cube?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2
\2
\2
\2
\2
\end{outline}
\end{multicols*}