\section{The Six Most Frequently Missed Errors on SAT Writing Multiple Choice: Strategies for Sentence Improvements and Sentence Errors}

\subsection{SAT Worksheet: Warm-Up}

\textit{Directions: Please order the following types of questions on the SAT writing section from 1 to 4 where 1 is the most difficult type of question for you and 4 is the least difficult types of questions for you.Then, do the example of Improving Sentences and Sentence Errors on the sheet.}

\bigskip
\underline{\hspace{2in}} \textbf{Improving Sentences}

\bigskip
The travel guide is useful because it covers not just reviews and photos, \ul{ but also tells you what and how to get to various destinations.}

\begin{enumerate}[label=(\Alph*)]
\item{but also tells you what and how to get to various destinations.}
\item{but also they gives ways of getting to various destinations.}
\item{but also advice of what and how to get to various destinations.}
\item{but also tells you what to do and how to get to various destinations.}
\item{and also tells you what to do and how to get to various destinations.}
\end{enumerate}

\bigskip
\underline{\hspace{2in}} \textbf{Sentence Errors}

\bigskip
\begin{inparaenum}[A]
Jean Rhys, \tfrac{whose}{\item} Dominican background \tfrac{has influenced}{\item} her writing, \tfrac{describes}{\item} many details of life in the Caribbean Islands \tfrac{vividly}{\item} in her novels and short stories. \tfrac{No Error}{\item}
\end{inparaenum}

\bigskip
\underline{\hspace{2in}} \textbf{Paragraph Improvements}

\bigskip
\underline{\hspace{2in}} \textbf{Essay}