\section{Word Choice}
The errors can be wrong words. These can be in the form of

\begin{itemize}
\item{idioms. What are idioms?} \hrulefill

Fill in the correct prepostion(s) after the verb:

\begin{enumerate}
\item to agree \hrulefill
\item to go ahead \hrulefill
\item to manage \hrulefill
\item to prefer \hrulefill
\item to prepare \hrulefill
\item to rebel \hrulefill
\item to rely \hrulefill
\item to be satisfied \hrulefill
\item to want \hrulefill
\end{enumerate}

\item{commonly confused words. For example, when do you use the word ``affect'' instead of ``effect''? } \hrulefill

\item{incorrect word choice.} 

Fill in the correct word(s) in the phrase. Then, write a sentence that uses the phrase correctly. The first one has been done as an example:

\begin{enumerate}
\item as \ldots \ul{as}
Sentence: The basketball player was as tall as the net.

 \item decide between \ldots \hrulefill 

\item either \dots \hrulefill
Sentence:

\item neither \ldots \hrulefill
Sentence:

\item not only \ldots \hrulefill
Sentence:

\item rather \ldots \hrulefill
Sentence:

\end{enumerate}
\end{itemize} 

\subsection{Practice SAT Questions}

\begin{enumerate}
\item \begin{inparaenum}[A]
The student \tfrac{wanted}{\item} \tfrac{both to}{\item} remain in Boston  \tfrac{or}{\item} move  \tfrac{to the West Coast}{\item} after graduation. \tfrac{No Error}{\item}
\end{inparaenum}

\item \begin{inparaenum}[A]
Over thirty million people were \tfrac{effected by}{\item} the snowstorm, and \tfrac{to this day}{\item}, many people are frightened when the \tfrac{news says}{\item} that there is a \tfrac{possibility of snow}{\item}. \tfrac{No Error}{\item}
\end{inparaenum}

\item \begin{inparaenum}[A]
\tfrac{After}{\item} waiting an hour for \tfrac{her}{\item} friend, the woman \tfrac{finally}{\item} arrived \tfrac{in}{\item} the theater. \tfrac{No Error}{\item}
\end{inparaenum}

\end{enumerate}



