\section{Verb Tense}

Verbs must agree with their subject in number. Many errors on the SAT writing section is related to subject-verb agreement and verb tense.
\subsection{Subject-Verb Agreement}

\begin{itemize}
\item{This is manageable when sentences are straightforward.}
\item{For example, fill in the following blanks: He \hrulefill smart. They \hrulefill smart.}
\item{To make the questions more difficult, the SATs will separate the subject and the verb with prepositional phrases or descriptions
with commas. An SAT question may also put
the verb before the subject.}
\item{For example: Stephen for more than two weeks \hrulefill happy because of his most recent grades. To solve
this type of question, identify the subject and cross out prepositional phrase. Then, identify
the correct verb form.}

\bigskip
Looking at it like this indicates that the subject is ``Stephen'' and so ``is'' is correct form of
the verb.

\item{For example: The group, consisting of two adults and five children, \hrulefill camping this weekend. To solve this type of question, identify the subject and cross out description (between the commas). Then, identify the correct verb form.}

\bigskip
The subject is ``the group'' and so ''is'' is correct form of the verb.

\item{For example: Running \hrulefill the girls' favorite sport. To solve this type of question, rearrange the sentence so that the subject comes before the verb. Then, identify the correct verb form.}

\bigskip
The sentence is re-arranged as ``'The girls' favorite sport \underline{\hspace{2in}} running.'' Therefore, the correct verb form is ``'is.''
\end{itemize}

