\section{Strategy: Eliminate Incorrect Answers then Find the Most Concise Answer}

On sentence improvements, the correct answer will be grammatically correct. Therefore, before
you see if an answer choice makes sense in the original sentence, determine if it is grammatically
correct. If not, then you can eliminate this right away.

In SAT sentence improvement problems, you should try to eliminate the 2-3 answer choices that are grammatically incorrect so that you are left with 2-3 other answer choices. The SAT sentence improvement section is looking for the "best" sentence, one that is concise and precise. In SAT world, this translates to the sentence that is not only grammatically correct AND concise. How does the SAT measure ``conciseness''? By length.

\bigskip
Therefore, the answer choice that you are looking for is grammatically correct and short without changing the meaning of the original sentence. The latter part means that it can not be so short that it is missing a key part of the original sentence,
but this is not usually an issue on sentence improvement problems.

\bigskip
Find the shortest answer. Then, check if it preserves the original meaning of the sentence by reading this answer choice in place of the underlined part of the original sentence. If so, this answer choice is the correct answer, so you should mark it.

\bigskip
\textit{Directions: Eliminate the answer choices that are grammatically incorrect for the following sentences. After you have eliminated an answer choice, write why it was incorrect on the line. Then, determine the correct answer using the strategy presented above. The first one has been done for you.}


<<<<<<< HEAD
\begin{enumerate}
\item The Boston Common is \ul{ older than it but still just as well-maintained as Central Park}.

\begin{enumerate}[label=(\Alph*)]
=======
\item The Boston Common is \ul{older than it but still just as well-maintained as Central Park}.
>>>>>>> 70cbfedac09602262caef6f421f9691f9f5a5fc2

\begin{enumerate}[label=(\Alph*)]
\item older than it but still just as well-maintained as Central Park 

  \ul{Eliminate because of ambiguous pronoun}
  
\item older than Central Park but just as well-maintained. 

\textbf{\ul{Correct. It is grammatically correct and the most concise.}}

\item  older than Central Park; it is just as well-maintained.   

  \ul{Eliminate because of ambiguous pronoun}
  
\item older and it is just as well-maintained as Central Park. 

\textbf{\ul{Grammatically correct but not as concise as (B).}}

\item just as comfortable as Central Park and it is older than it. \ul{Eliminate because of ambiguous pronoun}

\end{enumerate}

\bigskip
\item While most people detest high prices \ul{for food items, but organic food sells well despite the increased cost.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item for food items, but organic food sells well despite the increased cost. \hrulefill
 
\item for food items, organic food sells well despite the increased cost. \hrulefill
 
\item for food items, many people still purchase organic food despite the increased cost. \hrulefill

\item for food items, despite the increased cost, organic food sells well. \hrulefill
 
\item for food, but organic food sells well despite the increased cost. \hrulefill

\end{enumerate}

\bigskip
\item \ul{With determination and diligence, anyone can achieve a high score on the SAT test.}

\bigskip
\begin{enumerate}[label=(\Alph*)]

\item With determination and diligence, anyone can achieve a high score on the SAT test. \hrulefill
\item With determination and diligence, anyone is achieving a high score on the SAT test.\hrulefill
\item Anyone full of determination and diligence achieves a high score on the SAT test.\hrulefill
\item Determination and diligence can help anyone who wants to achieve a high score on the SAT test. \hrulefill
\item Anyone can achieve a high score on the SAT test with determination and diligence.\hrulefill
\end{enumerate}

\bigskip
\item The movie \ul{featured many well-respected actors and was winning many awards for} acting, directing, producing, and writing. 

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item featured many well-respected actors and was winning many awards for \hrulefill
\item featured many well-respected actors, was winning many awards for\hrulefill
\item featured many actors that were well-respected and won many awards for \hrulefill
\item had featured many well-respected actors and won many awards for\hrulefill
\item featured many well-respected actors and won many awards for \hrulefill
\end{enumerate}

\bigskip
\item \ul{Many educators believe that technology of the sort that} helps monitor student progress and deliever feedback to parents could be helpful in increasing test performance. 

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item Many educators believe that technology of the sort that \hrulefill
\item Many educators believe technology that \hrulefill
\item Many educators believe that technology which \hrulefill
\item A group of educators believe that technology that \hrulefill
\item Many educators believe that technology that \hrulefill
\end{enumerate}

\bigskip
\item After waiting an hour for her friend, the woman finally \ul{arrived in the theater donning a red dress.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item arrived in the theater donning a red dress.\hrulefill
\item donned a red dress and arrived in the theater. \hrulefill
\item arrived in the theater and donned a red dress. \hrulefill
\item arrived in the theater wearing a red dress.\hrulefill
\item arrived at the theater donning a red dress.\hrulefill
\end{enumerate}

\bigskip
\item Overjoyed that he was accepted his first choice college, \ul{Stephen is currently being slightly ridiculous.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item Stephen is currently being slightly ridiculous \hrulefill
\item Stephen is currently slightly ridiculous\hrulefill
\item Stephen is acting slightly ridiculous.\hrulefill
\item slightly rediculous Stephen is being. \hrulefill
\item currently Stephen is being slightly ridiculous.\hrulefill
\end{enumerate}

\bigskip
\item \ul{Many people think that Americans take the right to vote for granted, and I think that it is the right of Americans to not exercise their right to vote.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item Many people think that Americans take the right to vote for granted, and I think that it is the right of Americans to not exercise their right to vote. \hrulefill
\item Americans take the right to vote for granted according to many people, and I think that it is the right of Americans to not exercise their right to vote.\hrulefill
\item Many people think that Americans had taken the right to vote for granted, and I think that it is has been the right of Americans to not exercise their right to vote. \hrulefill
\item Many people think that Americans take the right to vote for granted, but I think that it is the right of Americans to not exercise their right to vote.\hrulefill
\item Americans take the right to vote for granted, yet it is the right of Americans to not exercise their right to vote.\hrulefill
\end{enumerate}

\bigskip
\item The bank robbers \ul{threatened the tellers by waving their guns, one of the criminals held a teller hostage} until the police arrived. 

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item threatened the tellers by waving their guns, one of the criminals held a teller hostage \hrulefill
\item threatened the tellers by waving their guns. One of the criminals held a teller hostage\hrulefill
\item threatened the tellers by waving their guns; one of the criminals held a teller hostage\hrulefill
\item waving their guns to threat the tellers. One of the criminals held a teller hostage\hrulefill
\item waved their guns to threat the tellers; one of the criminals held a teller hostage\hrulefill
\end{enumerate}

\bigskip
\item After a major political event such as September 11th, \ul{the president will address the nation, with his purpose being to inform and comfort the public.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item the president will address the nation, with his purpose being to inform and comfort the public. \hrulefill
\item the president will address the nation so that he can inform and comfort the public.\hrulefill
\item the president will address the nation to inform and comfort the public.\hrulefill
\item the president addresses the nation, with his purpose being to inform and comfort the public.\hrulefill
\item the president will address the nation, with the purpose to inform and comfort the public.\hrulefill
\end{enumerate}

\bigskip
\item Mary's secret, the whereabouts of the items that had been missing for weeks, \ul{were more compelling than Jeff's.}

\bigskip
\begin{enumerate}[label=(\Alph*)]
\item were more compelling than Jeff's. \hrulefill
\item were more compelling than Jeff's secret. \hrulefill
\item was more compelling than what Jeff said. \hrulefill
\item were more compelled than Jeff's. \hrulefill
\item was more compelling than Jeff's.\hrulefill
\end{enumerate}

\end{enumerate}
