\section{Pronouns}
Some common pronoun rules tested on the SAT Writing Section are agreement, unclear pronouns,
and inconsistent point of view.

\subsection{Agreement with the Antecedent}
\begin{enumerate}
\item{What is an antecedent?} \hrulefill
\item{Circle the antecedent and box the pronoun in the following sentence: Kenna the dog plays
with her favorite chew toys daily.}

\end{enumerate} 

\subsection{Unclear Pronouns}
Pronouns need to be clear regarding who or what they are referring to.
\begin{enumerate}
\item{Emily and Kate are going to her house today. Why is this sentence incorrect?} \hrulefill
\item{She is going to teach them today. Why is this sentence incorrect?} \hrulefill
\item{The amusement park rides are full of mice, therefore we will avoid them. Why is this sentence
incorrect?} \hrulefill
\item{Write a possible correction to the following sentence: The amusement park rides are full of
mice, therefore we will avoid them.} \hrulefill
\end{enumerate}

\subsection{Consistent Point of View}
Each sentence or paragraph needs to have the same point of view. For example, the following
sentence is incorrect: 

\bigskip
If one wants to go to the store, then I recommend that you find a driver.

\begin{itemize}
\item{\textbf{Correct:} If you want to want to go to the store, then I recommend that you find a driver.}
\item{\textbf{Another correct version of this sentence is,} If one wants to go to the store, I recommend that
one finds a driver.}
\item{Circle the following choice that makes the sentence correct: You\/one should never complain, even when one is given a difficult task.}
\item{Why is the answer that you circled correct?} \hrulefill
\end{itemize}