\section{SAT Worksheet: Warm-Up}

\textit{Directions: Read the question. If there's an error, identify the type of error (for example, a clause error). If you think the original phrasing produces a better sentence than any of the other alternatives, select choice A; if not, select one of the other choices.}

\begin{enumerate}

\item In order to apply for a job, a prospective employee must fill out an application, submit three letters of reference, and \ul{interviewing with the manager.}

\begin{enumerate}[label=(\Alph*)]
\item interviewing with the manager. 
\item to interview with the manager.
\item interview with the manager.
\item with the manager.
\item interview with the manager.
\end{enumerate}

\vfill\item 

\item The travel guide is useful because it offers not just reviews and photos, \ul{but also tells you what and how to get to various destinations.}
\begin{enumerate}[label=(\Alph*)]
\item but also tells you what and how to get to various destinations.
\item but also they gives ways of getting to various destinations.
\item but also advice of what and how to get to various destinations.
\item but also tells you what to do and how to get to various destinations.
\item and also tells you what to do and how to get to various destinations.
\end{enumerate}

\vfill\item


\item \underline{Like what happened with} other consulting firms, `'Gladiator Consulting'' also suffered during the economic recession.
\begin{enumerate}[label=(\Alph*)]
\item Like what happened with
\item As
\item Like
\item Like the case with
\item Despite
\end{enumerate}

\end{enumerate} 