\section{Determine the Type of Question You're Being Asked}

There are three main types of paragraph improvement questions:

\begin{enumerate}
\item{\large{\textbf{Grammar Revision}}}

These typically ask you for the best version of an underlined portion. 

\begin{itemize}
\item{For example: Which is the best version of the underlined portion of sentence 2 (repro-
duced below)?}

\item{The most common grammar errors that show in paragraph improvement are: run-on sentences, pronoun reference, misplaced modifiers, and subject-verb agreement.}
\end{itemize}

\item{\large{\textbf{Combination/Insertion}}}

These questions require you to choose the best way to insert or combine certain words and
sentences. They test your understanding of sentence relationships. There are many ways
one sentence can relate to the next. For example, one expresses a different view than the
other, one summarizes the other, one supports the other, and one presents a specific case of
the other.


Your job is to figure out the relationship and choose the answer that best expresses that
relationship.

\begin{itemize}
\item{TIP: Pay attention to leading phrases separated by commas. Not only are they the
most frequence place for transitions but they will also tell you the most about how one
sentence relates to the previous one.}
\end{itemize}

\item{\large{\textbf{Paragraph Relationship}}}

\begin{itemize}
\item{For example,}
\textit{Which of the following would be the best sentence to introduce the third paragraph?}
\begin{enumerate}[label=(\Alph*)]

\item        \ldots
\item   \ldots
\item    \ldots
\item    \ldots
\item   \ldots
\end{enumerate}

\end{itemize}

\end{enumerate}
