\section{Strategy \#4: Write a Clear, Two-Part Conclusion}

Conclusions consist of two parts, \textbf{re-stating the thesis} and \textbf{extending the argument.} The extension
is where you can demonstrate why your argument is important in a wider context than just your essay and consider the implications of the argument. For example, this can be suggestions of reasons or situations where people should consider your argument thoughtfully.

\bigskip
Samples of language for the extension in the conclusion may include:

\begin{itemize}
\item Based on this argument, society should consider \ldots
\item This argument suggestions that when \ldots occurs \ldots
\item Without considering this perspective, it is possible that \ldots
\end{itemize}


\subsection{SAT Worksheet: Practice Writing Conclusions}
\textit{Directions: For the theses and examples that you wrote in each of the two essay prompts in the
above worksheet, write a conclusion for each thesis and set of examples.}

\begin{enumerate}
\item \textbf{Assignment:} Is it better to accept and be happy with what you have, or to always seek greater sources of happiness? Plan and write an essay in which you develop your point of view on this issue. Support your position with reasoning and examples taken from your reading, studies, experience, or observations.

\vfill\item \textbf{Assignment:} In extolling the virtues of our freedom in schools, do we solidify freedom as a value to be protected, so do we teach children to be complacent about freedoms lost? Support your position with reasoning and examples taken from your reading, studies, experience, or observations.
\vfill
\end{enumerate}

