\section{Correcting Incorrect Answers}

While it can be frustrating to get a question wrong, it can be helpful to see why the answer that you selected was incorrect. Furthermore, understanding why the incorrect answers are incorrect can also alert you to the answer choices that the SAT question writers will use to try get you to select the incorrect answers.

\bigskip
\textbf{Why Incorrect SAT Answer Choices on the Passage-Based Reading Sections are Wrong}

\begin{enumerate}
\item\sloppy Too Broad/Require too much of a leap: Sometimes the passage is about a specific
example (like a mammal) and then the answer choice will be \shortline
(like about animals). The answer choice might feel right or that the statement may be
something the author would agree with, but it is usually not the best answer.

\item\sloppy Too narrow: This type of choice might be in the text, but \shortline
doesn't completely answer the question. This is common in questions about the \shortline
of the passage.

\item Too Extreme: The SAT want to test how carefully you can read and
a text. Therefore, words like \shortline, \shortline, \shortline, \shortline, \shortline, and \shortline are probably not good choices.

\item Not Stated in the Passage: The answer choice is not \shortline anywhere in the passage or is \shortline to the passage. This type of answer choice could make sense, but is not close enough to what is said in the passage.

\item True but unrelated to the Question: This type of answer choice might be \shortline
and \shortline but it doesn't \shortline the question.
\end{enumerate}
