\section{SAT Worksheet: Practice Determining SAT Words using Prefixes, Suffixes, and Roots}

\textit{Directions: Below is a list of roots and their definitions. Answer the question about the word that follows.}

\begin{enumerate}
\item Acer-, acid-, acri- means sharp. Based on this definition, if someone described a drink to you as ``acrid'', would you drink it? Why or why not? \hrulefill

\item Ag-, agi-, ig-, act- means do, move, or go. What will someone who is a poor navigator have trouble with? \hrulefill


\item Arch means chief, first, rule means. Do you think that American society is patriarchal or matriarchal? \hrulefill


\item Belli- means war. In what situation might someone be belligerent? \hrulefill

\item Carp-, cip-, cept means to take. How might this help you to figure out the definition of the word ``inception''? \hrulefill

\item Cred- means to \hrulefill. Name some credible news sources. \hrulefill

\item Dict- means to say or speak. What do you think that the word ``benediction'' means? \hrulefill (Hint: do you think that the prefix ``bene-'' refers to something good or something bad? \hrulefill

\item Duc-, duct- means to lead or to pull. If someone abducts someone else, what did they do? \hrulefill

\item Fac-, fact-, fic-, fect- means to do or make. What is currently not feasible without modern technology? \hrulefill

\item Fall-, fals- means to deceive. If someone is described as fallacious, would you want to be friends with them? \hrulefill

\item Fid-, fide-, feder- means faith or trust. If someone confides in you, what do they do? \hrulefill

\item Grad-, gress- means to bring together, to step or to go. How do you measure progress in your SAT class? \hrulefill

\item Greg- means herd. Where might a congregation of people meet? \hrulefill

\item Homo- means same whereas hetero- means different. What do you think that the word ``homophone'' means? \hrulefill (Hint: What do you think ``phon-'' means? \hrulefill

\item Jac-, Ject- means insert. What do you think is the goal of a projectile weapon? \hrulefill

\item Loqu-, locut- means to talk or to speak. Who is the most loquacious person in your class? \hrulefill

\item Magn- means great. Name a magnate in the technology industry. \hrulefill

\item Migra- means wander. How might you identify if a bird is migratory over a long period of time? \hrulefill

\item Neo- means new. Who do you know that has recently given birth to a neonate? \hrulefill

\item Oligo- means few or little. Do you think America is a democracy or an oligarchy? Why? \hrulefill

\item Pel-, puls- means drive or urge. What is a food that repulses you? \hrulefill

\item  Pon-, pos-, pound- means place or put. What do you think that postulate means? \hrulefill

\item Reg- or recti- means straighten. What is another word to describe someone that is ``regimented''? \hrulefill

\item Sacr-, sanc-, secr- means sacred. What do you think that the word sacrosanct means? \hrulefill

 \item  Sec-, sect- means to cut. How might you section a pizza? \hrulefill

 \item Sed-, sess-, sid means sit. What do you think that subsidiary means? \hrulefill
 
 \end{enumerate}