\section{Practice}

While it can be frustrating to get a question wrong, it can be helpful to see why the answer that
you selected was incorrect. Furthermore, understanding why the incorrect answers are incorrect
can also alert you to the answer choices that the SAT question writers will use to try get you to
select the incorrect answers.


\textbf{Why Incorrect SAT Answer Choices on the Passage-Based Reading Sections are
Wrong}

\begin{enumerate}
\item Too Broad/Require too much of a leap: Sometimes the passage is about a specific
example (like a mammal) and then the answer choice will be \underline{\hspace{2in}}
(like about animals). The answer choice might feel right or that the statement may be
something the author would agree with, but it is usually not the best answer.

\item Too narrow: This type of choice might be in the text, but \underline{\hspace{2in}}
doesnt completely answer the question. This is common in questions about the \underline{\hspace{2in}}
of the passage.

\item Too Extreme: The SATs want to test how carefully you can read and
a text. Therefore, words like , \underline{\hspace{2in}}, \underline{\hspace{2in}}, \underline{\hspace{2in}}, \underline{\hspace{2in}}, \underline{\hspace{2in}}, and \underline{\hspace{2in} are probably not good choices.

\item Not Stated in the Passage: The answer choice is not \underline{\hspace{2in}} anywhere in the passage or is \underline{\hspace{2in}} to the passage. This type of answer choice could make sense, but is not close enough to what is said in the passage.

\item True but unrelated to the Question: This type of answer choice might be \underline{\hspace{2in}}
and \underline{\hspace{2in}} but it doesn't \underline{\hspace{2in}} the question.

\end{enumerate}
