\section{Probability}

\textbf{General Equation}

\bigskip
\begin{equationbox}{Probability of Independent Events}
\renewcommand{\columnseprule}{0pt}
For independent events $A$ and $B$,

\begin{center}
\begin{multicols}{2}
$P_{A\mbox{ and }B}=P_A\cdot P_B$

$P_{A\mbox{ or }B}=P_A+P_B-P_{A\mbox{ and }B}$
\end{multicols}
\end{center}
\end{equationbox}

\bigskip
\begin{enumerate}[labelindent=*,style=multiline,leftmargin=*,label=\textbf{Example \arabic*:}]
\item Liang is playing a card game with a standard deck of playing cards. He wants the first card he picks up to be either a red card or a face card (Jack, Queen, or King). What is the probability he will choose either a red card or a face card?
\vfill\item Aurthur is choosing a number from 1 to 100 at random. What is the probability that he chooses a number that divisible by either 3 or 5?
\vfill\item Let $f(x)=|x|$ and $g(x)=x^2$. If $x$ is an integer in the interval from $-2$ to 2, what is the probability that a value of $x$ is in both the set of values for $f(x)$ and $g(x)$?
\end{enumerate}

\vfill
\newpage
\begin{multicols*}{2}
\begin{outline}[enumerate]
\medium

\1 If triangle ABC has side lengths of 1 and 3, what is the probability of choosing a possible integer side length in the integer set from 1 to 10?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0.2
\2 0.25
\2 0.3
\2 0.4
\2 0.5

\midline

\1 What is the probability of choosing at random an odd number from the set of remainders when a perfect square is divided by 8?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0
\2 1/8
\2 1/3
\2 2/3
\2 1/2

\columnbreak
\advanced

\1 The probability of $A$ happening is twice the probability of $B$ happening and the probability of $A$ or $B$ happening is twice the probability of $A$ happening. If the probability of $B$ happening is greater than 0, what is the probability of $A$ and $B$ happening?

\bigskip
\textbf{Equation/Strategy:} \hrulefill

\bigskip
\textbf{Solve:}

\vfill
\2 0.1
\2 0.2
\2 0.25
\2 0.5
\2 1

\midline

\1 Sherry enters a raffle at school. If she buys $x$ tickets, her chances of winning are 25\%. If she wants to increase her chances of winning to 40\%, what percentage of the original number of tickets sold will she need to purchase?

\bigskip
\textbf{Equation/Strategy:}

\bigskip
\textbf{Solve:}

\vfill
\2
\2
\2
\2
\2
\end{outline}
\end{multicols*}